---
title: "Assignment B1"
author: "Jackie"
date: "2023-10-30"
output: github_document
---
```{r}
library(testthat) #if testthat package is not already installed, run install.packages(testthat) prior
```

Exercise 1 and 2: 
The code chunk below contains both the function and documentation of the function that I have created for assignment B1.
```{r}
# Area of circle calculation 

# The function area_of_circle() is used to find the area of a circle when given the radius. This function only accepts numeric data greater than 0.  The function finds the square of the inputted radius and multiplies that by pi. 

# @param r is the radius of the circle in which the user is trying to find the area for. I named the parameter "r" because this is a common way of listing the radius of an object. 

# @return The output of the function is the area of a circle. Please note that the units for area are based on the units for the radius. If the radius is given in centimeters, the units for area will be cm^2. If the radius is given in meters, the units for area will be m^2. 

area_of_circle <- function(r) {stopifnot(is.numeric(r), r>0) 
    result <- pi*(r^2)
    paste("The area of a circle with radius", r, "is", pi*(r^2))}
```

Exercise 2: Below are three examples of my function (area_of_circle()) being put to use. 

Example 1. Find the area of a circle with given radius of 4. 
```{r}
print(area_of_circle(4))
```

Example 2. Run area_of_circle() function to see what happens when a character is inputted. 
```{r, error = TRUE}
print(area_of_circle("red"))
```

Example 3. Find area of a circle when given negative radius of -6. Note: a radius cannot be -6, I am just trying to show what happens when numeric data is inputted that does not fit the conditions of the code. 
```{r, error = TRUE}
print(area_of_circle(-3))
```

Exercise 4: Testing the function area_of_circle() using testthat package. 
```{r}
test_that("Testing area function", {
  expect_equal(area_of_circle(c(2, 3, 4)), c("The area of a circle with radius 2 is 12.5663706143592", "The area of a circle with radius 3 is 28.2743338823081", "The area of a circle with radius 4 is 50.2654824574367"))
  expect_error(area_of_circle(NA), regexp=NULL, class=NULL, "is.numeric(r) is not TRUE", inherit=TRUE, all=FALSE, info=NULL, label=NULL ) 
  expect_error(area_of_circle(0), regexp=NULL, class=NULL, "r > 0 is not TRUE", inherit=TRUE, all=FALSE, info=NULL, label=NULL) #using 0 as I would like to confirm that my function will recognize 0 as an improper value for a radius which must have a positive integer. 
})
```





